Redundant calibration as a complex optimization problem

### 2016-12-09 paper.tex
added some sparsity results

\begin{figure*}
\centering
\subfigure[$\gamma$]{\includegraphics[width=0.47\textwidth]{./sparsity.pdf}\label{fig:kappa}}
% V_R_3.pdf: 585x441 pixel, 72dpi, 20.64x15.56 cm, bb=0 0 585 441
\subfigure[$c$]{\includegraphics[width=0.46\textwidth]{./comp_order.pdf}\label{fig:cg_itr}}
\caption{In the left panel we plot the sparsity ratio $\gamma$ (the number of zero entries relative to the total number of entries in a matrix) of the Hessian $\bH$ as a function of the number 
of antennas $N$ in the array for different geometries, namely an hexagonal grid (blue circles), a square grid (green crosses) and a regular east-west grid (red circles). For the regular east-west grid we are able to construct an analytical expression for $\gamma$ (the dashed red line). Taking the limit 
of this expression, Eq.~\eqref{eq:gamma}, as $N\rightarrow \infty$ produces the black dotted line. In the right panel we plot the order of the computational cost $c$ for inverting $\bH$ as a function of the number 
of antennas in the array for different geometries. We use the same color scheme in the right and left panels. We compute $c$ using Eq.~\eqref{eq:c}. We can again compute 
an analytic expression (dashed red line) for the east-west grid using Eq.~\eqref{eq:c} and Eq.~\eqref{eq:gamma}.  
\label{fig:sup_anti}} 
\end{figure*}

>>>>

\begin{figure*}
\centering
\subfigure[$\gamma$]{\includegraphics[width=0.47\textwidth]{./sparsity.pdf}\label{fig:kappa}}
% V_R_3.pdf: 585x441 pixel, 72dpi, 20.64x15.56 cm, bb=0 0 585 441
\subfigure[$c$]{\includegraphics[width=0.46\textwidth]{./comp_order.pdf}\label{fig:cg_itr}}
\caption{In the left panel we plot the sparsity ratio $\gamma$ (the number of zero entries relative to the total number of entries in a matrix) of the Hessian $\bH$ as a function of the number 
of antennas $N$ in the array for different geometries, namely an hexagonal grid (blue circles), a square grid (green crosses) and a regular east-west grid (red circles). For the regular east-west grid we are able to construct an analytical expression for $\gamma$ (the dashed red line). Taking the limit 
of this expression, Eq.~\eqref{eq:gamma}, as $N\rightarrow \infty$ produces the black dotted line. In the right panel we plot the order of the computational cost $c$ for inverting $\bH$ as a function of the number 
of antennas in the array for different geometries. We use the same color scheme in the right and left panels. We compute $c$ using Eq.~\eqref{eq:c}. The red dashed line 
in the righ panel is associated with the theoretical curve of $c$ we computed for the east-west regular grid. The limit of the red-dashed curve is two, which we 
have plotted with a black dotted line.
\label{fig:sup_anti}} 
\end{figure*}
